\chapter{Conclusions and Future Work}
\label{ch:con}
\section{Conclusions}
In conclusion, our study presents a comprehensive evaluation of YOLO NAS models for automated blood cell identification and counting. The results demonstrate the effectiveness of deep learning-based object detection in streamlining the diagnostic process and improving the efficiency of blood cell analysis. Despite the challenges posed by varying hyperparameters and resource constraints, our findings underscore the potential of advanced machine learning techniques in revolutionizing medical diagnostics. 

\section{Future work}
Future research directions could focus on addressing the identified limitations and further enhancing the capabilities of automated blood cell analysis systems. This includes:



Dataset Augmentation: Expanding the annotated dataset through data augmentation techniques to improve model robustness and generalization.

\textbf{Model Optimization:}Investigating efficient model architectures and training strategies to reduce computational overhead while maintaining high performance.

\textbf{Real-world Deployment:} Conducting clinical validation studies to assess the real-world efficacy and usability of automated blood cell analysis systems in diverse healthcare settings.



Looking ahead, future research endeavors will focus on addressing the identified limitations and exploring novel avenues for advancing automated blood cell analysis systems. This includes further optimization of model architectures, leveraging transfer learning techniques for domain adaptation, and integrating additional modalities such as multi-modal imaging for comprehensive cell characterization. Additionally, collaboration with healthcare professionals and industry stakeholders will be essential for translating research findings into clinically impactful solutions.



This concludes our paper on "Automated Blood Cell Identification and Counting." We believe that the findings contribute to the ongoing efforts in leveraging technology to improve healthcare outcomes and look forward to the continued evolution of automated diagnostic tools in medical practice.


